Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2019-09-05 GWLDCII.tex
changes from over the phone

In Section~\ref{sec GN algorithm} we state an algorithm for constructing the Grassmann necklace of the positroid associated to a Wilson loop diagram (Algorithm~\ref{alg:put GN on WLD}) and prove its correctness (Theorem~\ref{res:alg gives GN}). While it was already possible to construct the Grassmann necklace of a Wilson loop diagram via existing bijections between some of the various combinatorial objects that index the positroid cells, this process was convoluted and involved multiple steps; our algorithm allows us to track directly how each propagator in the Wilson loop diagram contributes to each term in the Grassmann necklace. {\color{violet} Furthermore, the above algorithm allows us to determine that the positroids associated to Wilson loop better\note{This sentence has a grammar problem and perhaps as a consequence I don't understand what it is saying}. In particular, Corrollary \ref{no coloops} shows that these positroids have no coloops, and gives an exact characterization of their loops.}Many of the technical lemmas required to prove Theorem~\ref{res:alg gives GN} continue to be important in subsequent sections: in particular we have Lemma~\ref{lem sian}, which identifies certain configurations of propagators that must appear in any admissible Wilson loop diagram, and Lemma~\ref{vertex cyclic int lem}, which shows that the pattern of values that a propagator contributes to each term of the Grassmann necklace is both simple and predictable.

@@

\begin{dfn} \label{VPropdfn}
Let $W = (\cP, V)$ be a Wilson loop diagram.
\begin{enumerate}
\item For $p = (i,j) \in \cP$, let $V(p) = \{i, i+1, j, j+1\}$ denote the set of {\bf vertices supporting $p$}. For a set of propagators $P \subseteq \cP$, define 
\[V(P) = \bigcup_{p \in P} V(p)\]
to be the vertex support of $P$.
\item For $U \subseteq V$, the set of {\bf propagators supported on $U$} is denoted by
\[\Prop(U) = \{ p \in \cP\ |\ V(p) \cap U \neq \emptyset \}.\]
Note that a propagator in $\Prop(U)$ does not need to have its entire support contained in $U$. 
\item Vertices of $W$ that do not support any propagators are called {\bf non-supporting}. \st{The set of all non-supporting vertices in $W$ is denoted $F(\emptyset)$. }\sanote{tried to get rid of this notation. Check if I"ve missed any}
\end{enumerate}
\end{dfn}

@@

In this section we will give an algorithm (Algorithm~\ref{alg:put GN on WLD}) to go directly from a Wilson loop diagram to the Grassmann necklace of its positroid. This is a useful result in and of itself, as it greatly simplifies the process of identifying the positroid associated to a given Wilson loop diagram. {\color{violet} Furthemore, we use it to characterise the positroids associated to Wilson loop diagrams according to loops and coloops (Corrollary \ref{no coloops}).} It also allows us to examine how the positroid changes as we make minor changes to the Wilson loop diagram; indeed, the techniques we develop in this section to verify that our algorithm produces the correct Grassmann necklace will also be used repeatedly in later sections.

@@

The following lemma establishes certain configurations of propagators that must exist in any admissible diagram with no non-supporting vertices (i.e. with $F(\emptyset) = \emptyset$). We make use of this result in several induction proofs below.

\begin{lem}\label{lem sian} \sanote{should this be rephrased more similarly to the philosophy of Lemma 4.4, allowing non-supporting vertices to be added in or taken out?}
  Let $W$ be a weakly admissible WLD with at least 5 vertices and in which each vertex supports at least one propagator.  Then at least one of the following two things occurs:
  \begin{enumerate}
    \item $W$ has a propagator of length $\leq 6$ with a propagator of length 2 on one side of it and nothing else on that side.\label{item big and 2}
    \item There exists a pair of propagators of length $2$ with the property that the first propagator is $(i, i+2)$, the second is $(j, j+2)$, no other propagator ends between vertices $i+2$ and $j+1$, and $j\in\{i+2, i+3, i+4\}$.\label{item pair of 2s}
  \end{enumerate}
See Figure~\ref{fig: small configs} for an illustration of the two configurations.
\end{lem}

@@

With this setup, if we can find a vertex $\ell$ (with \hlfix{$\ell <_i i$ and $\ell <_m m$}{ $i <_i \ell$ and $m <_m \ell$? This is what is in the picture?}) such that the \emph{configuration} of propagators ending in the interval \st{$(j-1, \ldots, \ell+1)$} {\color{violet}$[j, \ell]$} is identical in both $W'$ and $V'$, then the vertices contributed to $I_i^W$ and $I_m^V$ are the same from step $j$ to step $\ell$ (inclusive). See Figure~\ref{fig:locally identical} for an illustration of this.

\begin{figure}
\[
\begin{tikzpicture}[baseline=(current bounding box.east)]
	\begin{scope}
	W' = \drawWLDfragment[12]{3}{0.4} 
	%\drawnumberspartial % use this to debug
	\newnode[left]{1}{i}
	\newnode[below]{4}{j}
	\newnode{5}{}
	\newnode{6}{}
	\newnode{7}{}
	\newnode{8}{}
	\newnode{9}{}
	\newnode{11}{}
	\newnode[right]{12}{l+1}
	\begin{scope}
		\clipcenterarc(0,0)(\startpoint-10:\endpoint+10:\radius)
		\newpropbend{6.3}{8.6}{80}
		\node at (\zero + 7.5*\step:\radius*0.8) {\footnotesize $r$};
		\newprop[midway,left]{5.5}{-4}{}
		\node at (\zero + 3*\step:\radius*0.5) {\footnotesize $p$};
		\newprop[midway]{11.5}{-4}{}
		\node at (\zero + 12.2*\step:\radius*0.7) {\footnotesize $q$};
	\end{scope}
\end{scope}
\end{tikzpicture}
\qquad \qquad
\begin{tikzpicture}[baseline=(current bounding box.east)]
	V' = \begin{scope}
	\drawWLDfragment[12]{3}{0.4} 
	%\drawnumberspartial % use this to debug
	\newnode[left]{2}{m}
	\newnode[below]{4}{j}
	\newnode{5}{}
	\newnode{6}{}
	\newnode{7}{}
	\newnode{8}{}
	\newnode{9}{}
	\newnode{11}{}
	\newnode[right]{12}{l+1}
	\begin{scope}
		\clipcenterarc(0,0)(\startpoint-10:\endpoint+10:\radius)
		\newpropbend{6.3}{8.6}{80}
		\node at (\zero + 7.5*\step:\radius*0.8) {\footnotesize $r$};
		\newprop[midway,left]{5.5}{19}{}
		\node at (\zero + 5.5*\step:\radius*0.5) {\footnotesize $s$};
		\newprop[midway]{11.5}{21}{}
		\node at (\zero + 11.8*\step:\radius*0.8) {\footnotesize $t$};
	\end{scope}
\end{scope}
\end{tikzpicture}
\]
\caption{$W'$ and $V'$ are locally the same between $j$ and $l+1$, so we will have $I_i^W\cap [j,l] = I_m^V\cap[j,l]$ even though $p \neq s$ and $q \neq t$.}\label{fig:locally identical}
\end{figure} \sanote{just checking, we are allowing the first and the last propagators (in the $I_i$ induced ordering) to be different, but not the internal ones?}\note{I think I see the problem here.  When I wrote $(j-1, \ldots, \ell+1)$ I meant the *list* from $j-1$ to $\ell+1$, so in particular $j-1$ and $\ell+1$ are included; it was not meant to be interval notation.  However, since we usually do use something more like interval notation we should write $[j-1, \ell+1]$.}

@@

So let $p = (a,b)$ with $a<_ib$ and $I_i(p) = b+1$, and choose $p$ such that $\big|[a+1,b]\big|$ is \hlfix{minimal amongst propagators of $W$ contributing their last vertices with this property.}{changed wording to be accurate, but feels clunky}

@@

Let $W = (\cP,[n])$ be an admissible Wilson loop diagram\st{, and}{\color{violet}. For every }$p = (i,j) \in \cP$\st{.  Then}{\color{violet}, the sets} $J_p^{W}(i)$, $J_p^{W}(i+1)$, $J_p^{W}(j)$, and $J_p^{W}(j+1)$ are each non-empty cyclic intervals which partition $[n]$ and occur in the given cyclic order.
\end{lem}
\sanote{is there a way to express the cyclic intervals more easily than the cases in this proof?}
\begin{proof}
We will prove the result by induction on the number of propagators.  If $W$ has one propagator then the result is immediate.  Now suppose $W$ has more than one propagator.  Since non-supporting vertices have no effect on Algorithm~\ref{alg:put GN on WLD}, it suffices to prove the result for $W$  (possibly weakly admissible) with \st{$F(\emptyset) = \emptyset$}{\color{violet} no non-supporting vertices}.  Then by Lemma~\ref{lem sian}, $W$ has at least one of the four situations illustrated in Figure~\ref{fig 3 cases}.

@@

In each of the four cases, when we remove the propagator labelled $p$ we obtain a diagram which satisfies \hlfix{the statement of the theorem by the induction hypothesis}{??? changed to statement of the theorem slightly to make this make sense}, and contains a propagator ${q = (i,j)}$ with no other propagators inside it (with respect to the $<_i$ orientation). Note that this region may or may not contain non-supporting vertices, which we will call $l, l+1, \ldots$ as necessary. Let $V$ be the diagram obtained by removing the propagator $p$ from $W$ (Figure \ref{fig V diagram}). $V$ is guaranteed to be an admissible diagram, since it was formed by removing a propagator from a diagram that was at least weakly admissible.

@@

We first calculate $I^{W}_w$ for a starting vertex ${w \in [n]\backslash \{l, l+1, \ldots,j,j+1\}}$. \hlfix{Note that $p$ has no effect on other propagators for starting vertices in this range,}{By rmk \ref{rmk algorithm locally same}? If so, the entire proof depends on this fact. We should state it prominently and move on.} so if $r \neq p$, then $I_w^W(r) = I_w^V(r)$. Meanwhile, the value of $I^{W}_w(p)$ depends on which step in the algorithm the propagator $q$ \hlfix{is assigned to}{did the change from assign to contribute never happen?} a vertex {\color{violet} in the diagram $V$}, i.e. on the value of $I^{V}_w(q)$. Thus, if $w\in J_q^{V}(i)$ then 
    \[
    I_w^{W}(r) =  \begin{cases}
        \max\{i+1, m\} & \text{if } r=p \\
        I_{w}^{V}(r) & \text{if } r\neq p
      \end{cases} 
    \]
    while if $w\in J_q^{V}(i+1)$ or $w\in J_q^{V}(j)$ then
    \[
    I_w^{W}(r) =  \begin{cases}
        l & \text{if } r=p \\
        I_{w}^{V}(r) & \text{if } r\neq p
      \end{cases} 
      \]
We also need to understand $I^{W}_w$ for $w \in \{l,l+1,\ldots,j,j+1\}$. For the majority 
%$w \in [l, l+a-1]$} 
%I left this as a comment so we can add it in if necessary, but I don't think we need this level of precision in this sentence: we're just signposting what we're going to do in detail shortly.
of these vertices, we use the following observation: if $p$ is the first propagator to be assigned a value by $I_w^{W}$, then the remainder of $I_w^{W}$ proceeds identically to the assignments of $I^{V}_{w+1}$ (recall Remark~\ref{rmk algorithm locally same}).  Thus we have for any $0\leq b <a$
    \[
    I_{l+b}^{W}(r) = \begin{cases}
      l+b & \text{if } r=p\\
      I_{l+b+1}^{V}(r) & \text{if } r\neq p
    \end{cases}
    \]
Similarly, if $j$ is in the support of $p$, then we have
     \[
       I_j^{W}(r) = \begin{cases}
         j & \text{if $r=p$ and $j$ is in the support of $p$}\\
         I_{j+1}^{V}(r) & \text{if $r\neq p$ and $j$ is in the support of $p$}\\
       \end{cases}
       \]
If $j$ is not in the support of $p$, then we must be in Case 2 of Figure~\ref{fig 3 cases} with two vertices in the right hand region.  In this case, if we start the algorithm at $j$ we need to know whether there will be any unassigned propagators other than $p$ when we reach vertex $i$, so as to know what $p$ contributes.

\sanote{skipping careful read of this proof and moving on}
Consider the Wilson loop diagram $X$ formed from $V$ by replacing the propagator $q = (i,j)$ with $q = (i, j-1)$;  $X$ is still admissible since we have not decreased the support of any set of propagators. 
% From the diagram we can see that $J_{j}^{V}(r) = J_{j}^{X}(r)$ for all $r\neq p$ (and in particular for $r=q$) and $J_{j}^{X}(r) = J_{j+1}^{X}(r)$ for $r\neq q,p$.  
It follows from the position of $q$ in $X$ that $I_j^X(q) = j$, and from Lemma~\ref{lem no fourth vertex} that $I_{j+1}^X(q) \neq j$. By the induction hypothesis, we must therefore have $I_{j+1}^X(q) = i$; in particular, this means that if we start at $j+1$ and assign propagators to vertices according to the algorithm, when we reach vertex $i$ in $X$ all propagators other than $q$ must have been assigned.

@@

Suppose for a contradiction that there exists an admissible diagram for which there exists an $i$ with $m\in I_i\setminus \{i\}$ and $m \not\in I_{i+1}$.  Fix $n$.  Let the triple $(W, i, m)$ be such a counterexample on $n$ vertices \hlfix{which is minimal with respect to the number of propagators}{minimal in what respect? $i$ first where this occurs? $m$ the smallest such number? what do propagators have to do with it?}. %, and among all those counterexamples on $n$ vertices with the same number of propagators, let $(W,i,k)$ be minimal with respect to the distance from $i$ to $k$ in the $\leq _i$ order.

@@

\textbf{Case I}:  Suppose $p$ has one end on edge $i-1$.  If $p$ is not supported on $i+1$, then in building $I_{i+1}$ we will assign the same propagators as in the construction of $I_i$ from vertices $i+1$ up to $b-1$, that is \bas I_{i+1} \cap [i+1,b-1] = I_{i} \cap [i+1,b-1]\eas {\color{violet}by Remark \ref{rmk algorithm locally same}}.  If $p$ is supported on $i+1$, then $b= i+1$ and the interval $[i+1,b-1]$ is empty, so the above equality remains true, albeit vacuously.  Furthermore, by Lemma~\ref{vertex cyclic int lem} it must happen that $p$ contributes vertex $b$ to $I_{i+1}$, as otherwise $b$ would never be contributed by $p$.  Consequently, by Remark \ref{clockwise ordering rem}, in building $I_{i+1}$,  when the algorithm reaches vertex $b$ there cannot be any remaining unassigned propagators that are supported on $b$ and clockwise of $p$.  This is also true in when the algorithm constructing $I_i$ reaches $b$, \st{since the same propagators have been assigned beforehand.}\sanote{don't like same here}{\color{violet}since any propagators lying counterclockwise of $p$ on the edge $i-1$ must have their support in $[i-1, b]$. By Lemma \ref{no fourth vertex}, these propagators contribute before the algorithm reaches $b$. Furthermore, Remark  \ref{rmk algorithm locally same} implies that these propagators contribute the same vertices to both $I_i$ and $I_{i+1}$.} This also implies that $m\geq_i b+1$.

@@

Combining Lemmas \ref{lem uncovered}, \ref{lem dihedral}, and \ref{lem good p}, it therefore suffices to study the Le diagrams of weakly admissible Wilson loop diagrams with \st{$F(\emptyset)  = \emptyset$}{\color{violet}no non-supporting vertices} and admitting one of the configurations described in Lemma \ref{lem good p}, with propagators $p = (n-3, n-1)$ and $q= (n-5, n-3)$ (if $q$ exists) both of length 2. See Figure~\ref{fig special p} for an illustration of the two possibilities.

>>>>

In Section~\ref{sec GN algorithm} we state an algorithm for constructing the Grassmann necklace of the positroid associated to a Wilson loop diagram (Algorithm~\ref{alg:put GN on WLD}) and prove its correctness (Theorem~\ref{res:alg gives GN}). While it was already possible to construct the Grassmann necklace of a Wilson loop diagram via existing bijections between some of the various combinatorial objects that index the positroid cells, this process was convoluted and involved multiple steps; our algorithm allows us to track directly how each propagator in the Wilson loop diagram contributes to each term in the Grassmann necklace. Furthermore, the above algorithm allows us to understand the positroids associated to Wilson loop better. In particular, Corollary \ref{no coloops} shows that these positroids have no coloops, and gives an exact characterization of their loops. Many of the technical lemmas required to prove Theorem~\ref{res:alg gives GN} continue to be important in subsequent sections: in particular we have Lemma~\ref{lem sian}, which identifies certain configurations of propagators that must appear in any admissible Wilson loop diagram, and Lemma~\ref{vertex cyclic int lem}, which shows that the pattern of values that a propagator contributes to each term of the Grassmann necklace is both simple and predictable.

@@

\begin{dfn} \label{VPropdfn}
Let $W = (\cP, V)$ be a Wilson loop diagram.
\begin{enumerate}
\item For $p = (i,j) \in \cP$, let $V(p) = \{i, i+1, j, j+1\}$ denote the set of {\bf vertices supporting $p$}. For a set of propagators $P \subseteq \cP$, define 
\[V(P) = \bigcup_{p \in P} V(p)\]
to be the vertex support of $P$.
\item For $U \subseteq V$, the set of {\bf propagators supported on $U$} is denoted by
\[\Prop(U) = \{ p \in \cP\ |\ V(p) \cap U \neq \emptyset \}.\]
Note that a propagator in $\Prop(U)$ does not need to have its entire support contained in $U$. 
\item Vertices of $W$ that do not support any propagators are called {\bf non-supporting}.
\end{enumerate}
\end{dfn}

@@

In this section we will give an algorithm (Algorithm~\ref{alg:put GN on WLD}) to go directly from a Wilson loop diagram to the Grassmann necklace of its positroid. This is a useful result in and of itself, as it greatly simplifies the process of identifying the positroid associated to a given Wilson loop diagram. Furthemore, we use it to characterize loops and coloops in the positroid associated to a Wilson loop diagram (Corrollary \ref{no coloops}). It also allows us to examine how the positroid changes as we make minor changes to the Wilson loop diagram; indeed, the techniques we develop in this section to verify that our algorithm produces the correct Grassmann necklace will also be used repeatedly in later sections.

@@

The following lemma establishes certain configurations of propagators that must exist in any admissible diagram with no non-supporting vertices. We make use of this result in several induction proofs below.

\begin{lem}\label{lem sian}
  Let $W$ be a weakly admissible WLD with at least 5 vertices and in which each vertex supports at least one propagator.  Then at least one of the following two things occurs:
  \begin{enumerate}
    \item $W$ has a propagator of length $\leq 6$ with a propagator of length 2 on one side of it and nothing else on that side.\label{item big and 2}
    \item There exists a pair of propagators of length $2$ with the property that the first propagator is $(i, i+2)$, the second is $(j, j+2)$, no other propagator ends between vertices $i+2$ and $j+1$, and $j\in\{i+2, i+3, i+4\}$.\label{item pair of 2s}
  \end{enumerate}
See Figure~\ref{fig: small configs} for an illustration of the two configurations.
\end{lem}

@@

With this setup, if we can find a vertex $\ell$ occurring after both $i$ and $m$ such that the \emph{configuration} of propagators ending in the interval $[j-1, \ell+1]$ is identical in both $W'$ and $V'$, then the vertices contributed to $I_i^W$ and $I_m^V$ are the same from step $j$ to step $\ell$ (inclusive). See Figure~\ref{fig:locally identical} for an illustration of this.

\begin{figure}
\[
\begin{tikzpicture}[baseline=(current bounding box.east)]
	\begin{scope}
	W' = \drawWLDfragment[12]{3}{0.4} 
	%\drawnumberspartial % use this to debug
	\newnode[left]{1}{i}
	\newnode[below]{4}{j}
	\newnode{5}{}
	\newnode{6}{}
	\newnode{7}{}
	\newnode{8}{}
	\newnode{9}{}
	\newnode{11}{}
	\newnode[right]{12}{l+1}
	\begin{scope}
		\clipcenterarc(0,0)(\startpoint-10:\endpoint+10:\radius)
		\newpropbend{6.3}{8.6}{80}
		\node at (\zero + 7.5*\step:\radius*0.8) {\footnotesize $r$};
		\newprop[midway,left]{5.5}{-4}{}
		\node at (\zero + 3*\step:\radius*0.5) {\footnotesize $p$};
		\newprop[midway]{11.5}{-4}{}
		\node at (\zero + 12.2*\step:\radius*0.7) {\footnotesize $q$};
	\end{scope}
\end{scope}
\end{tikzpicture}
\qquad \qquad
\begin{tikzpicture}[baseline=(current bounding box.east)]
	V' = \begin{scope}
	\drawWLDfragment[12]{3}{0.4} 
	%\drawnumberspartial % use this to debug
	\newnode[left]{2}{m}
	\newnode[below]{4}{j}
	\newnode{5}{}
	\newnode{6}{}
	\newnode{7}{}
	\newnode{8}{}
	\newnode{9}{}
	\newnode{11}{}
	\newnode[right]{12}{l+1}
	\begin{scope}
		\clipcenterarc(0,0)(\startpoint-10:\endpoint+10:\radius)
		\newpropbend{6.3}{8.6}{80}
		\node at (\zero + 7.5*\step:\radius*0.8) {\footnotesize $r$};
		\newprop[midway,left]{5.5}{19}{}
		\node at (\zero + 5.5*\step:\radius*0.5) {\footnotesize $s$};
		\newprop[midway]{11.5}{21}{}
		\node at (\zero + 11.8*\step:\radius*0.8) {\footnotesize $t$};
	\end{scope}
\end{scope}
\end{tikzpicture}
\]
\caption{$W'$ and $V'$ are locally the same between $j$ and $l+1$, so we will have $I_i^W\cap [j,l] = I_m^V\cap[j,l]$ even though $p \neq s$ and $q \neq t$.}\label{fig:locally identical}
\end{figure}

@@

So let $p = (a,b)$ with $a<_ib$ and $I_i(p) = b+1$, and choose $p$ such that $\big|[a+1,b]\big|$ is minimal amongst propagators of $W$ which contribute their last vertices and are in Case 2.

@@

Let $W = (\cP,[n])$ be an admissible Wilson loop diagram.  For every $p = (i,j) \in \cP$, the sets $J_p^{W}(i)$, $J_p^{W}(i+1)$, $J_p^{W}(j)$, and $J_p^{W}(j+1)$ are each non-empty cyclic intervals which partition $[n]$ and occur in the given cyclic order.
\end{lem}

\begin{proof}
We will prove the result by induction on the number of propagators.  If $W$ has one propagator then the result is immediate.  Now suppose $W$ has more than one propagator.  Since non-supporting vertices have no effect on Algorithm~\ref{alg:put GN on WLD}, it suffices to prove the result for $W$  (possibly weakly admissible) with no non-supporting vertices.  Then by Lemma~\ref{lem sian}, $W$ has at least one of the four situations illustrated in Figure~\ref{fig 3 cases}.

@@

In each of the four cases, when we remove the propagator labelled $p$ we obtain a diagram which satisfies the statement of the theorem by the induction hypothesis, and contains a propagator ${q = (i,j)}$ with no other propagators inside it (with respect to the $<_i$ orientation). Note that this region may or may not contain non-supporting vertices, which we will call $l, l+1, \ldots$ as necessary. Let $V$ be the diagram obtained by removing the propagator $p$ from $W$ (Figure \ref{fig V diagram}). $V$ is guaranteed to be an admissible diagram, since it was formed by removing a propagator from a diagram that was at least weakly admissible.

@@

We first calculate $I^{W}_w$ for a starting vertex ${w \in [n]\backslash \{l, l+1, \ldots,j,j+1\}}$. \hlfix{Note that $p$ has no effect on other propagators for starting vertices in this range,}{By rmk \ref{rmk algorithm locally same}? If so, the entire proof depends on this fact. We should state it prominently and move on.} so if $r \neq p$, then $I_w^W(r) = I_w^V(r)$. Meanwhile, the value of $I^{W}_w(p)$ depends on which step in the algorithm the propagator $q$ contributes a vertex in the diagram $V$, i.e. on the value of $I^{V}_w(q)$. Thus, if $w\in J_q^{V}(i)$ then 
    \[
    I_w^{W}(r) =  \begin{cases}
        \max\{i+1, m\} & \text{if } r=p \\
        I_{w}^{V}(r) & \text{if } r\neq p
      \end{cases} 
    \]
    while if $w\in J_q^{V}(i+1)$ or $w\in J_q^{V}(j)$ then
    \[
    I_w^{W}(r) =  \begin{cases}
        l & \text{if } r=p \\
        I_{w}^{V}(r) & \text{if } r\neq p
      \end{cases} 
      \]
We also need to understand $I^{W}_w$ for $w \in \{l,l+1,\ldots,j,j+1\}$. For the majority 
%$w \in [l, l+a-1]$} 
%I left this as a comment so we can add it in if necessary, but I don't think we need this level of precision in this sentence: we're just signposting what we're going to do in detail shortly.
of these vertices, we use the following observation: if $p$ is the first propagator to be assigned a value by $I_w^{W}$, then the remainder of $I_w^{W}$ proceeds identically to the assignments of $I^{V}_{w+1}$ (recall Remark~\ref{rmk algorithm locally same}).  Thus we have for any $0\leq b <a$
    \[
    I_{l+b}^{W}(r) = \begin{cases}
      l+b & \text{if } r=p\\
      I_{l+b+1}^{V}(r) & \text{if } r\neq p
    \end{cases}
    \]
Similarly, if $j$ is in the support of $p$, then we have
     \[
       I_j^{W}(r) = \begin{cases}
         j & \text{if $r=p$ and $j$ is in the support of $p$}\\
         I_{j+1}^{V}(r) & \text{if $r\neq p$ and $j$ is in the support of $p$}\\
       \end{cases}
       \]
If $j$ is not in the support of $p$, then we must be in Case 2 of Figure~\ref{fig 3 cases} with two vertices in the right hand region.  In this case, if we start the algorithm at $j$ we need to know whether there will be any unassigned propagators other than $p$ when we reach vertex $i$, so as to know what $p$ contributes.

Consider the Wilson loop diagram $X$ formed from $V$ by replacing the propagator $q = (i,j)$ with $q = (i, j-1)$;  $X$ is still admissible since we have not decreased the support of any set of propagators. 
% From the diagram we can see that $J_{j}^{V}(r) = J_{j}^{X}(r)$ for all $r\neq p$ (and in particular for $r=q$) and $J_{j}^{X}(r) = J_{j+1}^{X}(r)$ for $r\neq q,p$.  
It follows from the position of $q$ in $X$ that $I_j^X(q) = j$, and from Lemma~\ref{lem no fourth vertex} that $I_{j+1}^X(q) \neq j$. By the induction hypothesis, we must therefore have $I_{j+1}^X(q) = i$; in particular, this means that if we start at $j+1$ and assign propagators to vertices according to the algorithm, when we reach vertex $i$ in $X$ all propagators other than $q$ must have been assigned.

@@

Suppose for a contradiction that there exists an admissible diagram for which there exists an $i$ with $m\in I_i\setminus \{i\}$ and $m \not\in I_{i+1}$.  Fix $n$.  Let $W$ be such a counterexample with the minimal number of propagators.

@@

\textbf{Case I}:  Suppose $p$ has one end on edge $i-1$.  If $p$ is not supported on $i+1$, then in building $I_{i+1}$ we will assign the same propagators as in the construction of $I_i$ from vertices $i+1$ up to $b-1$, that is \bas I_{i+1} \cap [i+1,b-1] = I_{i} \cap [i+1,b-1]\eas by Remark \ref{rmk algorithm locally same}.  If $p$ is supported on $i+1$, then $b= i+1$ and the interval $[i+1,b-1]$ is empty, so the above equality remains true, albeit vacuously.  Furthermore, by Lemma~\ref{vertex cyclic int lem} it must happen that $p$ contributes vertex $b$ to $I_{i+1}$, as otherwise $b$ would never be contributed by $p$.  Consequently, by Remark \ref{clockwise ordering rem}, in building $I_{i+1}$,  when the algorithm reaches vertex $b$ there cannot be any remaining unassigned propagators that are supported on $b$ and clockwise of $p$.  This is also true in when the algorithm constructing $I_i$ reaches $b$, \st{since the same propagators have been assigned beforehand.}\sanote{don't like same here}{\color{violet}since any propagators lying counterclockwise of $p$ on the edge $i-1$ must have their support in $[i-1, b]$. By Lemma \ref{no fourth vertex}, these propagators contribute before the algorithm reaches $b$. Furthermore, Remark  \ref{rmk algorithm locally same} implies that these propagators contribute the same vertices to both $I_i$ and $I_{i+1}$.} This also implies that $m\geq_i b+1$.

@@

Combining Lemmas \ref{lem uncovered}, \ref{lem dihedral}, and \ref{lem good p}, it therefore suffices to study the Le diagrams of weakly admissible Wilson loop diagrams with no non-supporting vertices and admitting one of the configurations described in Lemma \ref{lem good p}, with propagators $p = (n-3, n-1)$ and $q= (n-5, n-3)$ (if $q$ exists) both of length 2. See Figure~\ref{fig special p} for an illustration of the two possibilities.
